Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-12-23 supplement.tex
work on fixing date at 60ka

Since a detailed model for the Out of Africa and Back-to-Africa was not our
main focus, we chose to keep this simplified model, but fix the split between
east African-European split at $50$ka. This allowed us to include Neanderthal
admixture into the OOA population at the previously-estimated $45$ka. Fixing
this parameter pushed back the estimated value for the split between the
ancestors of East and West African populations at around $60$ka, a value that
we took as fixed in most subsequent analyses. 
We discuss the sensitivity of our model to these assumptions in Section
\ref{sec:change-dates}.

\aprcomment{TODO: add (here?) our reasoning and validation of the choice of
60/50ka for fixed divergence times.}

>>>>

Since a detailed model for the Out of Africa and Back-to-Africa was not our
main focus, we chose to keep this simplified model, but fix the east
African-Eurasian split at $50$ka \aprcomment{references of archaeological
evidence of humans in Europe/near East by around 45ka}. This also allowed us to
include Neanderthal admixture into the OOA population at the
previously-estimated $45$ka \citep{}. Fixing these parameters (i.e., east
Africa-Eurasian split at 50ka, Neanderthal admixture at 45ka) resulted in an
estimated value for the split between the ancestors of East and West African
populations at around $60$ka.  \aprcomment{here: agrees with previous estimates
    of West African-European splits from LD \citep{Ragsdale2019-nt}, which used
    different populations from the Thousand Genomes Project than here. It is
    also in close alignment with inferred divergence times from an SFS-based
    demographic inference ($\sim65$ka), which used synonymous variation from a
subset of populations used in this study -- Mende (MSL), British (GBR), and Han
Chinese (CHB) (Section or Supp fig?).} We took this value (60ka) as fixed in
most subsequent analyses. We discuss the sensitivity of our model to these
assumptions in Section~\ref{sec:change-dates}.
